A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-01-28 paper.tex
Small edits

@@

>>>>

We compile interpolants into DNF cubes by constructing a temporary BDD. This
smaller representation is necessary for maintaining the size of formulas passed
to the SAT solver. However, it can occaisionally lead to state explosion.

@@

We presented an extension to an existing bounded synthesis technique that
promotes it to unbounded safety games. The approach taken as whole differs from
other synthesis techniques by combining counterexample guided game solving with
winning set computation. The results show that our approach is able to solve
more unique instances than other solvers by performing well on certain classes
of games that are hard for other methodologies.

Future work includes incorporating the solver into a parallel suite of
communicating solvers~\cite{bloem2014}. There is evidence that different
solvers perform well on different classes of games. Thus we hypothesise that
the way forward for synthesis tools is to combine the efforts of many different
techniques.

We also aim to experiment with optimisations by focusing on heuristics for
avoiding unhelpful actions as well as constructing succinct representations of
interpolants without resorting to BDDs.
